Article Title

### 2021-02-11 text/03-results.Rmd
add Fmax value and fix aspect names in tables

```{r annotation-quantities}
dt2 <- read.csv("../analyses/quantity/results/quantity_table.csv", header=T, stringsAsFactors=F)
# Format the genome names according to conventions
dt2$genome = format_genome(dt2$genome)
# Drop the absolute 'genes annotated' counts, we only want the percentual ones
dt2 <- dt2[, !names(dt2) %in% c("genes_annotated_c", "genes_annotated_f", "genes_annotated_p", "genes_annotated_a")]
headers_above = c(a = 3, b = 4, c = 4, d =4)
names(headers_above) <- c(" ", 
  paste0("Genes Annotated[\\\\%]", footnote_marker_alphabet(1, double_escape=T)), 
  paste0("Annotations", footnote_marker_alphabet(2, double_escape=T)),
  paste0("Median Ann. per G.", footnote_marker_alphabet(3, double_escape=T)))
kable(dt2, booktabs=T, digits=2, format.args=list(big.mark=","), escape=F, caption = "Quantitative metrics of the cleaned functional annotation sets. CC, BF, MP, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.", col.names=c("Genome", "Genes", "Dataset", "CC", "BF", "MP", "A","CC", "BF", "MP", "A","CC", "BF", "MP", "A")) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  add_header_above(headers_above, escape=F)%>%
  column_spec(c(15), bold = T) %>%
  column_spec(c(7,11), bold=T, border_right = T) %>%
  collapse_rows(columns = 1:2, latex_hline="major") %>%
  footnote(alphabet=c(
    "How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them? A = How many at least one from any aspect? ($\\\\textrm{A} = \\\\textrm{CC} \\\\cup \\\\textrm{BF} \\\\cup \\\\textrm{MP}$)",
    "How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\\\\textrm{A} = \\\\textrm{CC} + \\\\textrm{BF} + \\\\textrm{MP}$",
    "Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Please note that $\\\\textrm{A} \\\\neq \\\\textrm{CC} + \\\\textrm{BF} +\\\\textrm{MP}$"),
   general=c("\\\\href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quantity/results/quantity_table.csv}{Download this table (CSV)}"), general_title="", threeparttable=T, escape=F)
```

@@

```{r quality-table}
dt2 <- read.csv("../analyses/quality/results/quality_table.csv", header=T, stringsAsFactors=F)
dt2$genome = format_genome(dt2$genome)
headers_above = c(a = 2, b = 3, c = 3)
names(headers_above) <- c(" ", "SimGIC2", "TC-AUCPCR")
kable(dt2, booktabs=TRUE, escape=F, caption = "Quality evaluation of the used GO annotation sets.", col.names=c("Genome", "Dataset", "CC", "BF", "MP", "CC", "BF", "MP")) %>%
 kable_styling(latex_options = c("striped", "scale_down")) %>%
 add_header_above(headers_above, escape=F)%>%
 column_spec(c(5), border_right = T) %>%
 collapse_rows(columns = 1, latex_hline="major") %>%
 footnote(general=c("\\\\href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quality/results/quality_table.csv}{Download this table (CSV)}"), general_title="", threeparttable=T, escape=F)
```

>>>>

```{r annotation-quantities}
dt2 <- read.csv("../analyses/quantity/results/quantity_table.csv", header=T, stringsAsFactors=F)
# Format the genome names according to conventions
dt2$genome = format_genome(dt2$genome)
# Drop the absolute 'genes annotated' counts, we only want the percentual ones
dt2 <- dt2[, !names(dt2) %in% c("genes_annotated_c", "genes_annotated_f", "genes_annotated_p", "genes_annotated_a")]
headers_above = c(a = 3, b = 4, c = 4, d =4)
names(headers_above) <- c(" ", 
  paste0("Genes Annotated[\\\\%]", footnote_marker_alphabet(1, double_escape=T)), 
  paste0("Annotations", footnote_marker_alphabet(2, double_escape=T)),
  paste0("Median Ann. per G.", footnote_marker_alphabet(3, double_escape=T)))
kable(dt2, booktabs=T, digits=2, format.args=list(big.mark=","), escape=F, caption = "Quantitative metrics of the cleaned functional annotation sets. CC, MF, BP, and A refer to the aspects of the GO: Cellular Component, Molecular Function, Biological Process, and Any/All.", col.names=c("Genome", "Genes", "Dataset", "CC", "MF", "BP", "A","CC", "MF", "BP", "A","CC", "MF", "BP", "A")) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  add_header_above(headers_above, escape=F)%>%
  column_spec(c(15), bold = T) %>%
  column_spec(c(7,11), bold=T, border_right = T) %>%
  collapse_rows(columns = 1:2, latex_hline="major") %>%
  footnote(alphabet=c(
    "How many genes in the genome have at least one GO term from the CC, MF, BP aspect annotated to them? A = How many at least one from any aspect? ($\\\\textrm{A} = \\\\textrm{CC} \\\\cup \\\\textrm{MF} \\\\cup \\\\textrm{BP}$)",
    "How many annotations in the CC, MF, and BP aspect does this dataset contain? A = How many in total? $\\\\textrm{A} = \\\\textrm{CC} + \\\\textrm{MF} + \\\\textrm{BP}$",
    "Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Please note that $\\\\textrm{A} \\\\neq \\\\textrm{CC} + \\\\textrm{MF} +\\\\textrm{BP}$"),
   general=c("\\\\href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quantity/results/quantity_table.csv}{Download this table (CSV)}"), general_title="", threeparttable=T, escape=F)
```

@@

```{r quality-table}
dt2 <- read.csv("../analyses/quality/results/quality_table.csv", header=T, stringsAsFactors=F)
dt2$genome = format_genome(dt2$genome)
headers_above = c(a = 2, b = 3, c = 3, d = 3)
names(headers_above) <- c(" ", "SimGIC2", "TC-AUCPCR", "Fmax")
kable(dt2, booktabs=TRUE, escape=F, caption = "Quality evaluation of the used GO annotation sets.", col.names=c("Genome", "Dataset", "CC", "MF", "BP", "CC", "MF", "BP", "CC", "MF", "BP")) %>%
 kable_styling(latex_options = c("striped", "scale_down")) %>%
 add_header_above(headers_above, escape=F)%>%
 column_spec(c(5, 8), border_right = T) %>%
 collapse_rows(columns = 1, latex_hline="major") %>%
 footnote(general=c("\\\\href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quality/results/quality_table.csv}{Download this table (CSV)}"), general_title="", threeparttable=T, escape=F)
```
